Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?

### 2017-02-02 cloneoverflow-latex/cloneoverflow.tex
Moved Matheus to 2nd author.

\title{Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?}

\numberofauthors{1}
\author{
	\alignauthor
	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^1$Matheus Paixao, $^2$Giuseppe Bianco \\
	\affaddr{$^1$University College London, London, UK}\\
	\affaddr{$^2$Università degli Studi del Molise, Campobasso, Italy}
}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{outdated}
	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}
	\label{fig:outdated}
\end{figure}

>>>>

\title{Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?}

\numberofauthors{1}
\author{
	\alignauthor
	$^1$Chaiyong Ragkhitwetsagul, $^1$Matheus Paixao, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
	\affaddr{$^1$University College London, London, UK}\\
	\affaddr{$^2$Università degli Studi del Molise, Campobasso, Italy}
}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{outdated}
	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}
	\label{fig:outdated}
\end{figure}
